### 2021-09-19 README.Rmd
Minor edits

1. Download and install these fonts:
    - [Cochineal](https://fontesk.com/cochineal-typeface/)
    - [Assistant](https://fonts.google.com/specimen/Assistant)
    - [Linux Libertine O](https://www.cufonfonts.com/font/linux-libertine-o) (also [here](https://sourceforge.net/projects/linuxlibertine/))
    - [Libertinus Math](https://github.com/alerque/libertinus)
    - [InconsolataGo](https://github.com/ryanoasis/nerd-fonts/tree/master/patched-fonts/InconsolataGo)
      - If you're using Windows, make sure you right click on the font files and choose "Install for all users" when installing these fonts
2. [Install R](https://cloud.r-project.org/) (and preferably [RStudio](https://www.rstudio.com/products/rstudio/download/#download)).
    - If you're using macOS, [install XQuartz too](https://www.xquartz.org/) so that you have access to the Cairo graphics library
    - If you're using Windows, [install RTools too](https://cran.r-project.org/bin/windows/Rtools/) and add it to your PATH so that you can install packages from source if needed
3. Open `corrupt-caterpillar.Rproj` to open an [RStudio Project](https://r4ds.had.co.nz/workflow-projects.html).
4. Make sure you have a working installation of LaTeX:
    - *Easy-and-recommended way*: Install the [**tinytex** package](https://yihui.org/tinytex/) by running `install.packages("tinytex")` in the R console, then running `tinytex::install_tinytex()`. The first time you compile a PDF might require an extra minute or so while **tinytex** installs some missing LaTeX packages like csquotes, mathools, and others
    - *Easy-but-requires-huge-4+-GB-download way*: Download TeX Live ([macOS](http://www.tug.org/mactex/); [Windows](https://miktex.org/))
5. If it's not installed already, R *should* try to install the **renv** package when you open the RStudio Project for the first time. If you don't see a message about package installation, install it yourself by running `install.packages("renv")` in the R console.
6. Run `renv::restore()` in the R console to install all the required packages for this project.
7. Run `targets::tar_make()` in the R console to automatically download all data files, process the data, run the analysis, and compile the paper and appendix.

>>>>

1. Download and install these fonts (if you're using Windows, make sure you right click on the font files and choose "Install for all users" when installing these fonts):
    - [Cochineal](https://fontesk.com/cochineal-typeface/)
    - [Assistant](https://fonts.google.com/specimen/Assistant)
    - [Linux Libertine O](https://www.cufonfonts.com/font/linux-libertine-o) (also [here](https://sourceforge.net/projects/linuxlibertine/))
    - [Libertinus Math](https://github.com/alerque/libertinus)
    - [InconsolataGo](https://github.com/ryanoasis/nerd-fonts/tree/master/patched-fonts/InconsolataGo)
2. [Install R](https://cloud.r-project.org/) (and preferably [RStudio](https://www.rstudio.com/products/rstudio/download/#download)).
    - If you're using macOS, [install XQuartz too](https://www.xquartz.org/) so that you have access to the Cairo graphics library
    - If you're using Windows, [install RTools too](https://cran.r-project.org/bin/windows/Rtools/) and add it to your PATH so that you can install packages from source if needed
3. Open `corrupt-caterpillar.Rproj` to open an [RStudio Project](https://r4ds.had.co.nz/workflow-projects.html).
4. Make sure you have a working installation of LaTeX:
    - *Easy-and-recommended way*: Install the [**tinytex** package](https://yihui.org/tinytex/) by running `install.packages("tinytex")` in the R console, then running `tinytex::install_tinytex()`. The first time you compile a PDF might require an extra minute or so while **tinytex** installs some missing LaTeX packages like csquotes, mathools, and others, but after that, it'll go fast from then on.
    - *Easy-but-requires-huge-4+-GB-download way*: Download TeX Live ([macOS](http://www.tug.org/mactex/); [Windows](https://miktex.org/))
5. If it's not installed already, R *should* try to install the **renv** package when you open the RStudio Project for the first time. If you don't see a message about package installation, install it yourself by running `install.packages("renv")` in the R console.
6. Run `renv::restore()` in the R console to install all the required packages for this project.
7. Run `targets::tar_make()` in the R console to automatically download all data files, process the data, run the analysis, and compile the paper and appendix.
